Automated Metadata Generation for Fish Specimen Image Collections

### 2021-03-28 paper/paper.tex
Committing to pull
Tweaking Fish Image Analysis section and .bib entries

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
% \todo{Need to figure out what to actually do for this CCS stuff (\url{http://dl.acm.org/ccs.cfm}) and also the key words}
\begin{CCSXML}
<ccs2012>
   <concept>
       <concept_id>10002951.10002952.10003219.10003215</concept_id>
       <concept_desc>Information systems~Extraction, transformation and loading</concept_desc>
       <concept_significance>500</concept_significance>
   </concept>
   <concept>
        <concept_id>10010147.10010178</concept_id>
	<concept_desc>Computing methodologies~Artificial intelligence~Computer Vision</concept_desc>
	<concept_significance>500</concept_significance>
    </concept>
</ccs2012>
\end{CCSXML}

@@

Fish Classification\newline
Alsmadi 2010 \cite{Alsmadi2010FishRB},
Alsmadi 2019 \cite{Alsmadi2019RFE},
Hasija 2017 \cite{Hasija2017FishSC},
Hu 2012 \cite{HuJing2012Fscb},
Iqbal 2021 \cite{Iqbal2021AutomaticFS},
Iscimen 2014 \cite{Iscimen2014ImageAM},
Iscimen 2015 \cite{Iscimen2015ClassificationOF},

Orientation, Size and Weight and Shape\newline
Azarmdel 2019 \cite{Azarmdel2019DevelopingAO},
Balaban 2010 \cite{Balaban2010UsingIA},
Wang 2015 \cite{Huihui2015StudyOT},
Hao 2015 \cite{Hao2015TheMO},

Fish Quality\newline
Bernardo 2020 \cite{Bernardo2020FishQI},
Dowlati 2012 \cite{Dowlati2012ApplicationOM},

@@

Computer Vision Overviews to Fish\newline
G{\"u}m{\"u}ş 2011 \cite{Gm2011MachineVA},

Konovalov 2017 \cite{KonovalovD2017RDfA},
Williams 2020 \cite{Williams:2020:UIF},
Lalabadi 2020 \cite{Lalabadi2020FishFC},
Saberioon 2017 \cite{Saberioon2017ApplicationOM},
Tappi 2017 \cite{Tappi2017ComputerVS},
Taheri-Garavand 2019 \cite{TaheriGaravand2019RealtimeNM},
Konovalov 2018 \cite{Konovalov2018AutomaticSO},
Konovalov 2019 \cite{Konovalov2019AutomaticWE},
Lugatiman 2019 \cite{Lugatiman2019TunaMF},
Mu{\~n}oz-Benavent 2018 \cite{MuozBenavent2018EnhancedFB},
Petrov 2020 \cite{Petrov2020Overview},
Miranda 2017 \cite{MIRANDA201741},
Zion 2000 \cite{Zion2000InvivoFS},
Zion 2012 \cite{Zion2012ReviewTU},
Saitoh 2015 \cite{Saitoh2015ImagebasedFR},
Sung 2017 \cite{Sung2017VisionBR},
Sharmin 2019 \cite{Sharmin2019MVB},
Salman 2016 \cite{Salman2016FishSC},
Sung 2020 \cite{Sung2020AutomaticGF},
Xu 2021 \cite{Xu2021TransferLA},
Banan 2020 \cite{Banan2020Deep,LA}
Kinjo 2014 \cite{KinjoAtsushi2014Scoi},
Ogunlana 2015 \cite{Ogunlana2015FCU},
Sayed 2018 \cite{SayedGehadIsmail2018AAFS},
Rodrigues 2015 \cite{RodriguesMarcoT.A2015Ecda},
Shah 2019 \cite{Shah2019FishPakFS},
Li 2014 \cite{Li2014IdentificationOF}

@@

\section{Discussion}
\textbf{Todo}
\subsection{Future Work}
\begin{itemize}
    \item Further fine tuning of pixel analysis (e.g.\ thresholding on different regions of the bbox).
    \item Generalizing ruler reading.
    \item Training on a progressively larger number of image collections to hopefully gain reasonable generality for the whole class of fish specimen images.
    \item Adding things like seahorses and eels.
    \item Fitting a ``spine'' to specimen.
    \item Attempt to address tags that overlap fish? If nothing else could add a ``tag'' class and either try to exclude those pixels from the pixel analysis of the fish, or just use detectron bbox if a tag intersects with a specimen.
\end{itemize}
\section{Conclusion}
\textbf{Todo}

>>>>

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
\begin{CCSXML}
<ccs2012>
   <concept>
       <concept_id>10002951.10002952.10003219.10003215</concept_id>
       <concept_desc>Information systems~Extraction, transformation and loading</concept_desc>
       <concept_significance>500</concept_significance>
   </concept>
   <concept>
        <concept_id>10010147.10010178</concept_id>
	<concept_desc>Computing methodologies~Artificial intelligence~Computer Vision</concept_desc>
	<concept_significance>500</concept_significance>
    </concept>
</ccs2012>
\end{CCSXML}

@@

Fish Classification\newline
Alsmadi 2010 \cite{Alsmadi2010FishRB},
Alsmadi 2019 \cite{Alsmadi2019RFE},
Hasija 2017 \cite{Hasija2017FishSC},
Hu 2012 \cite{HuJing2012Fscb},
Iqbal 2021 \cite{Iqbal2021AutomaticFS},
Iscimen 2014 \cite{Iscimen2014ImageAM},
Iscimen 2015 \cite{Iscimen2015ClassificationOF},
Kinjo 2014 \cite{KinjoAtsushi2014Scoi},
Li 2014 \cite{Li2014IdentificationOF}

Orientation, Size and Weight and Shape\newline
Azarmdel 2019 \cite{Azarmdel2019DevelopingAO},
Balaban 2010 \cite{Balaban2010UsingIA},
Wang 2015 \cite{Huihui2015StudyOT},
Hao 2015 \cite{Hao2015TheMO},
Konovalov 2018 \cite{Konovalov2018AutomaticSO},
Konovalov 2019 \cite{Konovalov2019AutomaticWE},

Ruler Detection\newline
Konovalov 2017 \cite{KonovalovD2017RDfA},

Fish Quality\newline
Bernardo 2020 \cite{Bernardo2020FishQI},
Dowlati 2012 \cite{Dowlati2012ApplicationOM},
Lalabadi 2020 \cite{Lalabadi2020FishFC},

@@

Computer Vision Overviews Related to Fish\newline
G{\"u}m{\"u}ş 2011 \cite{Gm2011MachineVA},

Williams 2020 \cite{Williams:2020:UIF},
Saberioon 2017 \cite{Saberioon2017ApplicationOM},
Tappi 2017 \cite{Tappi2017ComputerVS},
Taheri-Garavand 2019 \cite{TaheriGaravand2019RealtimeNM},
Lugatiman 2019 \cite{Lugatiman2019TunaMF},
Mu{\~n}oz-Benavent 2018 \cite{MuozBenavent2018EnhancedFB},
Petrov 2020 \cite{Petrov2020Overview},
Miranda 2017 \cite{MIRANDA201741},
Zion 2000 \cite{Zion2000InvivoFS},
Zion 2012 \cite{Zion2012ReviewTU},
Saitoh 2015 \cite{Saitoh2015ImagebasedFR},
Sung 2017 \cite{Sung2017VisionBR},
Sharmin 2019 \cite{Sharmin2019MVB},
Salman 2016 \cite{Salman2016FishSC},
Sung 2020 \cite{Sung2020AutomaticGF},
Xu 2021 \cite{Xu2021TransferLA},
Banan 2020 \cite{Banan2020Deep,LA}
Ogunlana 2015 \cite{Ogunlana2015FCU},
Sayed 2018 \cite{SayedGehadIsmail2018AAFS},
Rodrigues 2015 \cite{RodriguesMarcoT.A2015Ecda},
Shah 2019 \cite{Shah2019FishPakFS},

@@

\section{Discussion}
\textbf{Todo}: Will need some sort of intro/framing paragraph
\subsection{Results}\todo{Just going to put the results discussion in small sections and we can change it later if that doesn't make sense}
\subsubsection{Object Detection}
\begin{itemize}
    \item Worked fairly well all things considered
    \item Talk about which fish failed
    \item Talk about which rulers failed
\end{itemize}
\subsubsection{Side Detection}

\subsubsection{Clock Value}

\subsubsection{Brightness?}

\subsubsection{Bounding Box}

\subsubsection{Length}

\subsection{Future Work}
\begin{itemize}
    \item Further fine tuning of pixel analysis (e.g.\ thresholding on different regions of the bbox).
    \item Generalizing ruler reading.
    \item Training on a progressively larger number of image collections to hopefully gain reasonable generality for the whole class of fish specimen images.
    \item Adding things like seahorses and eels.
    \item Fitting a ``spine'' to specimen.
    \item Attempt to address tags that overlap fish? If nothing else could add a ``tag'' class and either try to exclude those pixels from the pixel analysis of the fish, or just use detectron bbox if a tag intersects with a specimen.
\end{itemize}
\section{Conclusion}
\textbf{Todo}
